Approximation as Differentiation: Notes

### 2025-05-20 main/formal-structures.tex
Tweaks.

We noted that $\LatGal$ is $\CMon$-enriched (actually $\SemiLat$-enriched) and moreover that the product of
lattices is also a coproduct, making $\LatGal$ into a category with \emph{biproducts}. In fact having
biproducts is sufficient to ensure $\CMon$-enrichment; such a category is called \emph{semi-additive}.

@@

The product/coproduct is called a \emph{biproduct}, and the biproduct structure is denoted by $(\biprod, 0)$.
The unit $0$ is both terminal and initial and is called a \emph{zero} object. \todo{State the biproduct
``laws'' that follow from this formulation.} A semi-additive category $\cat{C}$ is enriched in $\CMon$, the
category of commutative monoids: for any two morphisms $f, g: X \to Y$ in $\cat{C}$, the biproduct structure
provides a way to ``add'' them together, forming a morphism $f + g: X \to Y$. Diagrammatically:

>>>>

We noted that $\LatGal$ is enriched in $\CMon$, the category of commutative monoids (in fact in $\SemiLat$)
and moreover that the product of lattices is also a coproduct, making $\LatGal$ into a category with
\emph{biproducts}. In fact the presence of biproducts is sufficient for $\CMon$-enrichment; such a category is
called \emph{semi-additive}.

@@

The product/coproduct is called a \emph{biproduct}, with the biproduct structure denoted by $(\biprod, 0)$.
The unit $0$ is both terminal and initial and is called a \emph{zero} object. \todo{State the biproduct
``laws'' that follow from this formulation.} A semi-additive category $\cat{C}$ is enriched in $\CMon$: for
any two morphisms $f, g: X \to Y$ in $\cat{C}$, the biproduct structure provides a way to ``add'' them
together, forming a morphism $f + g: X \to Y$. Diagrammatically:
